Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-24 main.tex
bogovskii operator

We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, and we have 
\[
    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
\]
The space $W^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\[
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \quad 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\]
We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
They are defined by 
\begin{subequations}\label{eq_definition_piola}
\begin{align}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
    \phi^{\divergence}(\bfw) &= \left( \frac{ \Jacobian\phi^{-1} }{\det\Jacobian\phi^{-1}} \bfw \right)  \circ \phi, \\
    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
\end{align}
\end{subequations}
where $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$, 
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
These mappings are invertible. 
%
% TODO: bounds
%
We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
    \\
    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
    % TODO: watch the sign 
    \\
    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
\end{align}
\end{subequations}
for $v \in W^{p}(\grad,\Omega)$, $\bfv \in W^{p}(\curl,\Omega)$, and $\bfw \in W^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{1,p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{1,p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
    \end{CD}
\end{align*}

@@

% Copied from McIntosh paper 
Rewriting $B^{k}$ in the same way, we get
\begin{equation}\label{eq:Bogo}
    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da\;.
\end{equation}
If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
one sees that $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$, 
and that $B^{k} u(x) = 0$ unless $x \in \Omega$. 
Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
Since $\Omega$ is bounded, $u \in C^{\infty}_{\overline\Omega}(\bbR^{n},\Alt^{k})$ implies $\supp B^{k} u \subset\overline\Omega$. 
The fact that $B^{k}$ indeed maps 
$C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.

>>>>

We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, and we have 
\[
    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
\]
The space $W^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\[
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \quad 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\]
We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
They are defined by 
\begin{subequations}\label{eq_definition_piola}
\begin{align}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
    \phi^{\divergence}(\bfw) &= \left( \det(\Jacobian\phi) \Jacobian\phi^{-1} \bfw \right)  \circ \phi, \\
    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
\end{align}
\end{subequations}
where $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$, 
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
These mappings are invertible. 
%
% TODO: bounds
%
We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
    \\
    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
    % TODO: watch the sign 
    \\
    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
\end{align}
\end{subequations}
for $v \in W^{p}(\grad,\Omega)$, $\bfv \in W^{p}(\curl,\Omega)$, and $\bfw \in W^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{1,p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{1,p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
    \end{CD}
\end{align*}

@@

% Copied from McIntosh paper 
We begin with introducing the Costabel-McIntosh-Bogovski\u{\i} kernel.
For $\ell\in\{0,\dotsc,n\}$, we define the kernel $G_\ell : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}
\label{eq:Gl}
  G_\ell(x,y) = 
  \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt \;.
\end{equation}
Given a differential form $u \in {C^\infty}_0(\bbR^n,\Alt^\ell)$, \(1\leq \ell \leq n\), 
we then define the integral operators
\begin{align}
  T_\ell u(x) &= \int G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
\end{align}
We call $T_\ell$ a Bogovski\u{\i}-type operator.

In order to see that the integrals in the definition of $T_\ell$ exist, 
we first rewrite the kernel $G_\ell$:
\begin{align*}
    G_\ell(x,y) 
    &= 
    \int_0^\infty \tau^{n-\ell} (\tau+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+\tau(x-y) \right)\,d\tau
    \\
    &= 
    \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} 
    \int_0^\infty \tau^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+\tau(x-y) \right)\,d\tau 
    \\
    &= 
    |\Omega|^{-1}\sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \,
    |x-y|^{k-n} \int_0^\infty r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr \;
    .
\end{align*}
We can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
\begin{align*}
    G_\ell(x,y) 
    &\leq 
    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_0^D r^{n-k-1} \,dr \;.
    \\
    &= 
    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
\end{align*}
We pointwise estimate $B_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| B_{\ell} u(x) \right|
    &=
    \left| 
        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \left| 
        \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \right| 
    \\&\leq 
    \left| 
        \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
    \right| 
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_D(0)} |z|^{k+1-n} dz
    =
    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
    =
    \vol_{n-1}(S_1) \int_0^D r^{k} dr
    =
    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
    .
\end{align*}
We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \\&
    =
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    =
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A(n,\ell) \leq 2^{\ell-1}}
    .
\end{align*}
So the convolution of $u$ is taken against an integrable function. 
Taylor's inequality now implies: 
\begin{align*}
    \| B_{\ell} u \|_{L^{p}(\Omega)}
    &\leq 
    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
In particular, we have a bounded operator $B_{\ell} : L^{p}(\bbR^n,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1})$ for any $1 \leq p \leq \infty$.

\newpage 
In order to see other properties of the operators, we apply a different change of variables. 
Let us write this in detail for the operator $R_\ell$. 
We substitute $y$ by the new variable $a=y+t(x-y)$.
Whence $da = (1-t)^n dy$ and $t(x-y) = a-y$ and $x-y = (a-y)/t$ and $x - (a-x)/t = y$
\begin{align*}
    T_\ell u(x) 
    &= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\&= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+(x-y)-(x-y)+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\&= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(x+(t+1)(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} (t+1)^{n}
    \chi_{\Omega}\left(a\right) 
    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
\end{align*}
Then we substitute $1-s = 1/(t+1)$, that is, $s = t/(t+1)$:
Whence $t = \left( 1/s-1 \right)^{-1}$.
\begin{align*}
    T_\ell u(x) 
    &= 
    \int \int_1^\infty (t-1)^{n-\ell} \left( 1/s-1 \right)^{\ell-1} (t+1)^{n}
    \chi_{\Omega}\left(a\right) 
    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
    \\
    &= 
    .
\end{align*}

Then we substitute $s = (t-1)/t$:
\begin{align*}
    &= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{-n+\ell-1} 
    \chi_{\Omega}\left(a\right)
    \frac{(a-y)}{t} \lrcorner u(x+(a-x)/t) \,dt\,da 
    \\
    &= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
    .
\end{align*}
Then we substitute $s = (t-1)/t$:
\begin{align*}
    T_\ell u(x) 
    &= 
    \int \int_1^\infty s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
    \\
    &= 
    - \int \int_1^\infty s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
    \\
    &=
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
We copy a statement by McIntosh and Costabel, who are too fucking lazy to write down their goddamn substititions for fucks sake, stupid assholes:
\begin{align*}
    T_\ell u(x) 
    = 
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $T_\ell u(x)$ is smooth with support contained in $\overline\Omega$ as well.

We compute the exterior derivative of this potential:
\begin{align*}
    T_{\ell,a} u(x) 
    &= 
    (x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    \\&
    = 
    (x-a)\lrcorner 
    \sum_{\sigma \in \Sigma(k,n)}
    \int_1^\infty 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
    \\&
    = 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
    \int_1^\infty 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
    .
\end{align*}
\begin{align*}
    \cartan T_{\ell,a} u(x) 
    &= 
    k
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
    \int_1^\infty 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
    \\&\qquad
    + 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
    \int_1^\infty 
    t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
    .
\end{align*}
When we calculate the exterior derivative of $u$, we find 
\begin{align*}
    \cartan u(x)
    =
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \partial_{j} u(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
    .
\end{align*}
The potential operator, applied to this result, gives 
\begin{align*}
    T_{\ell+1,a} \cartan u(x)
    &=
    (x-a)\lrcorner 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
    \cartanx^{j} \wedge \cartanx^{\sigma}
    \\&
    = 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
    \cartanx^{\sigma}
    - 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
    (-1)^{i-1}
    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
    .
\end{align*}
We add the exterior derivative of the potential and the potential of the exterior derivative.
Applying cancelations, we find 
\begin{align*}
    &
    \cartan T_{\ell,a} u(x)
    +
    T_{\ell+1,a} \cartan u(x)
    \\&
    =
    k
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
    \int_1^\infty 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
    \\&\qquad
    + 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
    \int_1^\infty 
    t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
    \\&\qquad
    +
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
    \cartanx^{\sigma}
    \\&\qquad
    - 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
    (-1)^{i-1}
    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
    \\&
    =
    \ell
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
    \int_1^\infty 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
    \\&\qquad
    +
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
    \cartanx^{\sigma}
    \\&
    =
    \sum_{\sigma \in \Sigma(k,n)} 
    \int_1^\infty \partial_{t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
    \\&
    =
    \sum_{\sigma \in \Sigma(k,n)} 
    u_{\sigma}\left(x)\right) \cartanx^{\sigma}
    =
    u(x)
    .
\end{align*}

From this form of $T_\ell$, because of the unbounded interval of integration in $t$, one cannot immediately conclude that $T_\ell$ maps ${C^\infty}$ functions to ${C^\infty}$ functions.
But if $u\in{C^\infty}_0(\bbR^n,\Alt^\ell)$, one sees that $T_\ell u$ is ${C^\infty}$ on 
$\bbR^n\setminus\supp\chi_{\Omega}$, and that 
$T_\ell u(x)=0$ unless $x$ lies in the starlike hull of $\supp u$ with respect to $B$. 
Thus if $\Omega$ is open and starlike with respect to $B$, then   
$u\in{C^\infty}_0(\Omega,\Alt^\ell)$ implies $\supp T_\ell u \subset\Omega$, and, if $\Omega$ is bounded, then
$u\in{C^\infty}_{\overline\Omega}(\bbR^n,\Alt^\ell)$ implies $\supp T_\ell u \subset\overline\Omega$. 
The fact that $T_\ell$ indeed maps 
${C^\infty}_0(\bbR^n,\Alt^\ell)$ to ${C^\infty}_0(\bbR^n,\Alt^{\ell-1})$ will be a consequence of Theorem~\ref{T:pseudo} below.

\subsection{Homotopy relations}

Cartan's formula for the Lie derivative of a differential form with respect to a vector field can be written as
$$
  \frac{d}{dt}F^*_t u = F^*_t \left(d(X_t\lrcorner u) + X_t\lrcorner du\right)\;,
$$
where $F^*_t$ denotes the pull-back by the flow $F_t$ associated with the vector field $X_t$. Here we consider the special case of the dilation flow with center $a$
$$
  F_t(x) = a+t(x-a) \quad\text{ with vector field } X_t=x-a\;,
$$
which gives a pull-back of
$$
  F^*_t u(x) = t^\ell \,u\left(a+t(x-a)\right) \quad \text{for an $\ell$-form } u \;.
$$
This leads to the formula
\begin{equation}
\label{eq:Cartan}
 \frac{d}{dt}(t^\ell u\left(a+t(x-a)\right) =
    d\Bigl(t^{\ell-1}(x-a)\lrcorner u\left(a+t(x-a)\right)\Bigr) +
    t^{\ell}(x-a)\lrcorner du\left(a+t(x-a)\right)
\end{equation}
which can also be verified elementarily from the formulas we gave in Section~\ref{S:notation}.

Integrating \eqref{eq:Cartan} from $0$ to $1$ and comparing with \eqref{eq:regPoincare}, 
we find the homotopy relations, valid for all $u\in{C^\infty}_0(\bbR^n,\Alt^\ell)$ 
\begin{equation}
\begin{aligned}
\label{eq:dR+Rd=1}
 dR_\ell u + R_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
 R_1 du &= u - \left(\chi_{\Omega},u\right)\; &&(\ell=0)\;;\\
 dR_nu &=u &&(\ell=n)\;.
\end{aligned}
\end{equation}
One could be tempted to integrate Cartan's formula from $1$ to $\infty$ and compare with \eqref{eq:Bogo}, thus formally obtaining a similar homotopy relation for $T_\ell$ directly. The result is indeed true except for $\ell=n$, but for a rigorous proof we prefer to use the duality relation \eqref{eq:dualRT} to deduce corresponding anticommutation relations for $T_\ell$ from the relations \eqref{eq:dR+Rd=1} which are already proved. Here is what one obtains for $u\in{C^\infty}_0(\bbR^n,\Alt^\ell)$:
\begin{equation}
\begin{aligned}
\label{eq:dT+Td=1}
  dT_\ell u + T_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
  T_1 du &= u \; &&(\ell=0)\;;\\
 dT_n u &=u - (\int\! u)\star\chi_{\Omega}&&(\ell=n)\;.
\end{aligned}
\end{equation}
Here we consider $\chi_{\Omega}$ as an element of ${C^\infty}_0(\bbR^n,\Alt^0)$, so that for another $0$-form $u$ we have the $L^2$ scalar product $\left(\chi_{\Omega},u\right)=\int\chi_{\Omega}(a)u(a)da$, and $\star\chi_{\Omega}$ is the $n$-form $\chi_{\Omega}(x)dx_1\wedge\dots\wedge dx_n$.

The formulas for the endpoints $\ell=0$ and $\ell=n$ correspond to the two extended de Rham complexes without boundary conditions and with compact support, see \eqref{eq:edRwobc} and \eqref{eq:edRwcs}. To see this, let us extend the definition of the exterior derivative by writing $\overline d$ for all the mappings of the complex
$$
 0 \to\bbR\to^\iota{C^\infty}(\overline\Omega,\Alt^0) \to^d {C^\infty}(\overline\Omega,\Alt^1)
 \to^d\cdots \to^d {C^\infty}(\overline\Omega,\Alt^n) \to 0
$$ 
and $\underline d$ for all the mappings of the complex
$$
 0 \to {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^0) \to^d {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^1) \to^d\cdots
 \to^d {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^n) \to^{\iota^*} \bbR \to 0
$$
where $\iota$ is the inclusion mapping for constant functions and 
$\iota^*=(\star\iota)'$ denotes the integral $u\mapsto\int\!u$ for $n$-forms.

If we correspondingly extend the definitions of $R_\ell$ and $T_\ell$ by
$$
\begin{aligned}
  R_0u &:=\left(\chi_{\Omega},u\right)\,\text{ for $0$-forms }u\,, &
  R_{n+1} &:=0\,,\\
  T_{n+1}u &:= \star(u\chi_{\Omega}) \,\text{ for }u\in\bbR\,,  &
  T_0 &:= 0\,,
\end{aligned}
$$
then we can write the relations \eqref{eq:dR+Rd=1} and \eqref{eq:dT+Td=1} simply as
\begin{equation}\label{eq:R&T&d}
 \overline d\,R_\ell u + R_{\ell+1} \,\overline d u  = u
 \quad \text{ and }\quad
 \underline d\,T_\ell u + T_{\ell+1} \,\underline du = u\quad \text{ for all }\;
  0\le\ell\le n.
\end{equation}

\begin{lemma}
    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. Then 
    \begin{align*}
        \| \vec u \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \vec u \|_{L^{2}(\Omega)}.
    \end{align*}
\end{lemma}
\begin{proof}
    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
    with smallest singular value $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
    which has the same smallest singular value. 
\end{proof}
